Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-10 article/article.Rmd
Commit 2024-09-10 19:11

```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11. The green line with blue symbols depicts the measured GHI in one-minute steps. The red line shows the modeled threshold for the detection of CE events, which are denoted with gray circles. The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with red circles. The purple line is the modeled cloud-free irradiance. The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical dashed lines.", fig.pos='H'}
knitr::include_graphics("../images/P-example-day-5.png")
```

>>>>

```{r example-day, echo=FALSE, fig.cap="Example of CE identification in Thessaloniki for 2019-07-11. The green line with blue symbols depicts the measured GHI in one-minute steps. The red line shows the modeled threshold for the detection of CE events, which are denoted with red circles. The black line represents the TOA TSI on a horizontal plane, equivalent to the threshold for the identification of ECE events, shown with magenta circles. The purple line is the modeled cloud-free irradiance. The dark yellow line is the solar constant of $1367\\,\\text{W}/\\text{m}^{2}$. The three sky images below the figure are taken at three characteristic instances (a, b, c) denoted on the figure with vertical orange dashed lines.", fig.pos='H'}
knitr::include_graphics("../images/P-example-day-3.png")
```
